results

### 2023-02-24 results_work.RMD
small fig updates

**Figure 1:** A) Overview of the experimental design with 12 days of concomitant dietary intervention and resistance training (RT), preceded by 7 days of testing. Familiarization = days -7 to -1 included familiarization to RT exercises (via 1RM leg press and knee extension tests) and strength tests (Humac dynamometer) at days -7 and -5. Baseline strength tests were conducted at day -1. Biopsies were taken from vastus lateralis at baseline (Day 1 leg 1, Day 2 leg 2) and after five RT sessions (Day 11 leg 1, Day 12 leg 2). The order in which participants performed the two intervention blocks was determined in a planned randomized fashion, where one leg was randomized to RT with GLU (glucose) and the other to RT with PLA (placebo). The randomization also entailed half starting with GLU (n = 8) and the other half with PLA (n = 8), in addition they where further randomized to start either with their dominant or non-dominant leg. Thus, 4 participants were randomized to start RT with their dominant leg and GLU supplement, and 4 with their non-dominant leg and GLU - the same was true for participtants commencing the intervention with PLA. From intervention start (Day 1 leg 1, Day 2 leg 2), the participants exercised in a unilateral, alternating fashion until post intervention testing (Day 11/12 leg 1, Day 12/13 leg 2). Three participants dropped out of the intervention, either due to reported muscular discomforts to heavy strength training or sickness in the family. B and C) Changes in Plasma glucose (mmol/L) and -c-peptide levels (pmol/L) during RT session six (Day 11 leg 1, Day 12 leg 2). Finger draws and venous blood were sampled at baseline (Day -1), as well as before, during and after session six. Plasma glucose was measured via finger draws, 120 (-120), 90 (-90) and 30 (-30) minutes and immediately before RT (0), during RT (15), immediately after (30) and 2hrs after RT (120). Levels of c-peptide were measured via venous blood samples collected at the same time points as finger draws, except for 90min before RT and during RT. D, E, F) Changes in muscular performance (D: nm fold change in isometric peak torque, E/F: nm fold change in isokinetic peak torque at 60/240 d/s.). Muscular performance was measured via a Humac Norm Dynamometer at baseline (Day -1), during (Day 4 and 8 leg 1, Day 5 and 9 leg 2), and after five RT sessions (Day 11 leg 1, Day 12 leg 2). G, H, I) Changes in muscular recovery (G: nm fold change in isometric peak torque, H/I: nm fold change in isokinetic peak torque at 60/240 d/s). Muscular recovery was measured via Humac Norm Dynamometer with baseline being post fifth RT session test, and then 30min, 2hrs and 23hrs following the sixth and final RT session. Values are presented as estimated marginal means ± 95% CI. * = *p* < 0.05 between groups. Glucose n = 13, placebo n = 13.

@@

###### **Figure 2:** Changes in total RNA and ribosomal RNA. A) Total RNA, B) 47S pre-rRNA, C) 18S rRNA, D) 28S rRNA, E) 5.8S rRNA, F) 5S rRNA. Baseline = Training day 1/2, Post = Training day 11/12. Total RNA and rRNA were analyzed in duplicates, with two duplicates per biopsy (two biopsies per time point). Total RNA and rRNA changes were calculated as log-fold change score per mg wet muscle weight. Mean change scores of the duplicates were calculated before modelling and transformed to the log-scale. Values are estimated marginal means fold change per leg per supplement ± 95% CI. p = between groups statistic, glucose compared to placebo. Glucose n = 13, placebo n = 13.

@@

###### **Figure 3:** Changes in levels of protein. A) rPS6, B) c-Myc, C) UBF. Baseline = Training day 1/2, Post = Training day 11/12. Protein samples were analyzed in duplicates, with two duplicates per biopsy (two biopsies per time point). The duplicates were loaded on different gels, in an inverted order. Change in protein levels were calculated as log-fold change score normalised by pools (pools of all protein samples). Mean change scores of the duplicates were calculated before modelling and transformed to the log-scale. Values are estimated marginal means fold change per leg per supplement ± 95% CI. * = significant between groups statistic, glucose compared to placebo. Glucose n = 13, placebo n = 13.

>>>>

**Figure 1:** A) An overview of the experimental design with 12 days of concomitant dietary intervention and resistance training (RT), preceded by 7 days of testing. Familiarization = days -7 to -1 included familiarization to RT exercises (via 1RM leg press and knee extension tests) and strength tests (Humac dynamometer) at days -7 and -5. Baseline strength tests were conducted at day -1. Biopsies were taken from vastus lateralis at baseline (Day 1 leg 1, Day 2 leg 2) and after five RT sessions (Day 11 leg 1, Day 12 leg 2). The order in which participants performed the two intervention blocks was determined in a planned randomized fashion, where one leg was randomized to RT with GLU (glucose) and the other to RT with PLA (placebo). The randomization also entailed half starting with GLU (n = 8) and the other half with PLA (n = 8), in addition they where further randomized to start either with their dominant or non-dominant leg. Thus, 4 participants were randomized to start RT with their dominant leg and GLU supplement, and 4 with their non-dominant leg and GLU - the same was true for participtants commencing the intervention with PLA. From intervention start (Day 1 leg 1, Day 2 leg 2), the participants exercised in a unilateral, alternating fashion until post intervention testing (Day 11/12 leg 1, Day 12/13 leg 2). Three participants dropped out of the intervention, either due to reported muscular discomforts to heavy strength training or sickness in the family. B and C) Changes in Plasma glucose (mmol/L) and -c-peptide levels (pmol/L) during RT session six (Day 11 leg 1, Day 12 leg 2). Finger draws and venous blood were sampled at baseline (Day -1), as well as before, during and after session six. Plasma glucose was measured via finger draws, 120 (-120), 90 (-90) and 30 (-30) minutes and immediately before RT (0), during RT (15), immediately after (30) and 2hrs after RT (120). Levels of c-peptide were measured via venous blood samples collected at the same time points as finger draws, except for 90min before RT and during RT. D) Changes in muscular performance/recovery measured as isometric and isokinetic peak torque (60 and 240 d/s) via Humac Norm Dynamometer, conducted at baseline (Day -1), during the intervention (Day 4 and 8 leg 1, Day 5 and 9 leg 2), after five RT sessions/before the 6th session (Day 11 leg 1, Day 12 leg 2), as well as 30min, 2hrs and 23hrs after the 6th RT session (Day 11/12 leg 1, Day 12/13 leg 2). Values are presented as estimated marginal means ± 95% CI. * = *p* < 0.05 between groups. Glucose n = 13, placebo n = 13.

@@

###### **Figure 2:** Changes in total RNA and ribosomal RNA. A) Total RNA, B) 47S pre-rRNA, 18S rRNA, 28S rRNA, 5.8S rRNA, 5S rRNA. Baseline = Training day 1/2, Post = Training day 11/12. Total RNA and rRNA were analyzed in duplicates, with two duplicates per biopsy (two biopsies per time point). Total RNA and rRNA changes were calculated as log-fold change score per mg wet muscle weight. Mean change scores of the duplicates were calculated before modelling and transformed to the log-scale. Values are estimated marginal means fold change per leg per supplement ± 95% CI. p = between groups statistic, glucose compared to placebo. Glucose n = 13, placebo n = 13.

@@

###### **Figure 3:** Changes in levels of protein. A) Representative total protein stain blot, B) AU fold change in UBF, c-Myc and rpS6 + representative antibody stain images of the respective proteins. Baseline = Training day 1/2, Post = Training day 11/12. Protein samples were analyzed in duplicates, with two duplicates per biopsy (two biopsies per time point). The duplicates were loaded on different gels, in an inverted order. Change in protein levels were calculated as log-fold change score normalised by pools (pools of all protein samples). Mean change scores of the duplicates were calculated before modelling and transformed to the log-scale. Values are estimated marginal means fold change per leg per supplement ± 95% CI. * = significant between groups statistic, glucose compared to placebo. Glucose n = 13, placebo n = 13.
